Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-01-29 paper/elsarticle/main.tex
Review: Some further TODOs

@@

			\textcolor{red}{[ TODO: Please, checkthe  word limit. ]}

@@

>>>>

			\textcolor{red}{[ TODO: Please, emphasize the chemical engineering viewpoint, especially in Sec.4. ]}

			\textcolor{red}{[ TODO: Please, extend the Control setup, as there is missing e.g., the initial laboratory temperature, the identification procedure of the system model, etc. ]}

@@

			\textcolor{red}{[ TODO: Please, check the word limit of Abstract. ]}

@@

	\textcolor{red}{[ TODO: How about the following table notation? ]}

	\begin{table}[h!]
		\begin{center}
			\caption{Control performance criteria.}
			\label{tab:control_performance}
			\begin{tabular}{c|c|c|c|c|c} 
				Reference step change & Explicit MPC controller & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
				\hline
				\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 714 & 33.50 & 16.5 & \textbf{2.12} \\
				& damped & 867 & 16.65 & 12.5 & 2.36 \\ 
				& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
				\hline
				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & aggressive & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
				& damped & 606 & 23.25 & 26.5 & 3.19 \\ 
				& self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
				\hline
				\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
				& damped & 398 & 79.64 & 31 & \textbf{2.00} \\ 
				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
				\hline
				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & aggressive & 1024 & 18.43 & 22.5 & 0.94 \\
				& damped & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10 
			\end{tabular}
		\end{center}
	\end{table}
